---
title: "Homework 2"
author: "Erika Park"
date: "9/28/2021"
output: github_document
---

```{r, warning = F, message=F}
library(dplyr)
library(nycflights13)
``` 
#### 1. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?



#### 2. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
flights %>% select(dep_time, sched_dep_time)
``` 

```{r}
flights %>% 
  mutate(dep_minutes_since_midnight = (dep_time %/% 100)* 60 + (dep_time %%100),
         sched_minutes_since_midnight = (sched_dep_time %/% 100) * 60 + (sched_dep_time %% 100)) #%>% View
``` 


#### 3. Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()

