---
title: "Week 3: Homework 2"
author: "Erika Park"
date: "9/28/2021"
output: github_document
---

link to github: https://github.com/ErikaPark/433_hw2/blob/main/hw2_ErikaPark.md

```{r, warning = F, message=F}
library(dplyr)
library(nycflights13)
library(ggplot2)
``` 

#### 1. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

* The flights with missing dep_time also have missing arr_time. 
* Since both departure time and arrival time are missing for the flights, it seems like the flights are the cancelled flights.
* Since there are 8255 rows, there seem to be 8255 cancelled flights. 

```{r}
filter(flights, is.na(dep_time))
```


\vspace{10pt}

#### 2. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

* We need to split out the numbers.
* We first need to divide by 100 and discard the remainder. The number would represent the hours. The number needs to be multiplied by 60 to convert to minutes. 
* The remainder would be the minutes. 
* Midnight is represented by 2400, which is 1440 minutes. This should correspond to 0. 

\vspace{10pt}

```{r}
flights %>%  
  mutate(dep_time_mins = (dep_time %/% 100 * 60 + dep_time %% 100) %% 1440,
  sched_dep_time_mins = (sched_dep_time %/% 100 * 60 + sched_dep_time %% 100) %% 1440) %>% 
  select(dep_time, dep_time_mins, sched_dep_time,sched_dep_time_mins)
``` 

\vspae{10pt}

#### 3. Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()

\vspace{10pt}

* One pattern that I noticed with the data is that with the total number of flights each day, the number of cancelled flights rises.

```{r, warning=F, message = F}
flights %>%
  mutate(cancelled = (is.na(arr_delay) | is.na(dep_delay))) %>%
  group_by(year, month, day) %>%
  summarise(
    cancelled = mean(cancelled),
    av_dep_delay = mean(dep_delay, na.rm = T),
    av_arr_delay = mean(arr_delay, na.rm = T)
  ) %>% 
  ggplot(aes(x = av_dep_delay, y = cancelled)) + geom_point()

``` 

*  By looking at the plot, strong relationship is visible between average departure delay and proportion of cancelled flights. 
* Except a few outliers, we can see that the departure delay is positively related to the proportion of cancelled flights. 












